---
title: "Potential Impacts of Pesticides in Florida and California"
author: "Zhenwei Weng"
date: "2024-10-21"
output: pdf_document
---
```{r}
library(dplyr)

straw<-read.csv("straw_eda.csv")

straw <-straw %>%
  mutate(Value = na_if(Value, "(D)")) %>%
  mutate(Value = na_if(Value, "(NA)")) %>%
  mutate(Value = as.numeric(Value)) %>%
  filter(!is.na(Value) & is.finite(Value))
data_ins <- straw %>%
  filter(type == "INSECTICIDE")

data_fun <- straw %>%
  filter(type == "FUNGICIDE")

data_her <- straw %>%
  filter(type == "HERBICIDE")

data_other <- straw %>%
  filter(type == "OTHER")

ins_1 <- data_ins %>%
  filter(measure == "LB / ACRE / YEAR")

ins_2 <- data_ins %>%
  filter(measure == "NUMBER")

ins_3 <- data_ins %>%
  filter(measure == "LB / ACRE / APPLICATION")

ins_4 <- data_ins %>%
  filter(measure == "LB")

ins_5 <- data_ins %>%
  filter(measure == "PCT OF AREA BEARING")

fun_1 <- data_fun %>%
  filter(measure == "LB / ACRE / YEAR")

fun_2 <- data_fun %>%
  filter(measure == "NUMBER")

fun_3 <- data_fun %>%
  filter(measure == "LB / ACRE / APPLICATION")

fun_4 <- data_fun %>%
  filter(measure == "LB")

fun_5 <- data_fun %>%
  filter(measure == "PCT OF AREA BEARING")


herb_1 <- data_her %>%
  filter(measure == "LB / ACRE / YEAR")

herb_2 <- data_her %>%
  filter(measure == "NUMBER")

herb_3 <- data_her %>%
  filter(measure == "LB / ACRE / APPLICATION")

herb_4 <- data_her %>%
  filter(measure == "LB")

herb_5 <- data_her %>%
  filter(measure == "PCT OF AREA BEARING")

other_1 <- data_other %>%
  filter(measure == "LB / ACRE / YEAR")

other_2 <- data_other %>%
  filter(measure == "NUMBER")

other_3 <- data_other %>%
  filter(measure == "LB / ACRE / APPLICATION")

other_4 <- data_other %>%
  filter(measure == "LB")

other_5 <- data_other %>%
  filter(measure == "PCT OF AREA BEARING")


library(ggplot2)
library(patchwork)

plot_metric <- function(data, title) {
  if (nrow(data) == 0 || !("Value" %in% names(data)) || sum(!is.na(data$Value)) == 0) {
    return(ggplot() + 
             labs(title = paste(title, "(No Data Available)")) +
             theme_void())
  }
  
  ggplot(data, aes(x = State, y = as.numeric(Value), fill = State)) +
    geom_boxplot() +
    labs(title = title, x = "State", y = "Usage (Value)") +
    theme_minimal()
}
```

Plots for FUNGICIDE

```{r}
ins_1_plot <- plot_metric(ins_1, "fungicide-LB/ACRE/YEAR")
ins_2_plot <- plot_metric(ins_2, "fungicide-NUMBER")
ins_3_plot <- plot_metric(ins_3, "fungicide-LB/ACRE/APPLICATION")
ins_4_plot <- plot_metric(ins_4, "fungicide-LB")
ins_5_plot <- plot_metric(ins_5, "fungicide-PCT OF AREA BEARING")
insecticide_plots <- (ins_1_plot | ins_2_plot | ins_3_plot) /
                     (ins_4_plot | ins_5_plot)
print(insecticide_plots)
```


Plots for Insecticide

```{r}
fun_1_plot <- plot_metric(fun_1, "Insecticide-LB/ACRE/YEAR")
fun_2_plot <- plot_metric(fun_2, "Insecticide-NUMBER")
fun_3_plot <- plot_metric(fun_3, "Insecticide-LB/ACRE/APPLICATION")
fun_4_plot <- plot_metric(fun_4, "Insecticide-LB")
fun_5_plot <- plot_metric(fun_5, "Insecticide-PCT OF AREA BEARING")
fungicide <- (fun_1_plot | fun_2_plot | fun_3_plot) /
                     (fun_4_plot | fun_5_plot)

print(fungicide)
```
Plots for Heribicide
```{r}
herb_1_plot <- plot_metric(herb_1, "Herbicide-LB/ACRE/YEAR")
herb_2_plot <- plot_metric(herb_2, "Herbicide-NUMBER")
herb_3_plot <- plot_metric(herb_3, "Herbicide-LB/ACRE/APPLICATION")
herb_4_plot <- plot_metric(herb_4, "Herbicide-LB")
herb_5_plot <- plot_metric(herb_5, "Herbicide-PCT OF AREA BEARING")

herbicide_plots <- (herb_1_plot | herb_2_plot | herb_3_plot) /
                   (herb_4_plot | herb_5_plot)
print(herbicide_plots)
```

Plots for Other chemical type
```{r}
other_1_plot <- plot_metric(other_1, "Other-LB/ACRE/YEAR")
other_2_plot <- plot_metric(other_2, "Other-NUMBER")
other_3_plot <- plot_metric(other_3, "Other-LB/ACRE/APPLICATION")
other_4_plot <- plot_metric(other_4, "Other-LB")
other_5_plot <- plot_metric(other_5, "Other-PCT OF AREA BEARING")

other_plots <- (other_1_plot | other_2_plot | other_3_plot) /
               (other_4_plot | other_5_plot)
print(other_plots)
```


Setup for GHS searcher and harzard retriever
```{r}
library(tidyverse)
library(PubChemR)
GHS_searcher<-function(result_json_object){
  result<-result_json_object
  for (i in 1:length(result[["result"]][["Hierarchies"]][["Hierarchy"]])){
    if(result[["result"]][["Hierarchies"]][["Hierarchy"]][[i]]
       [["SourceName"]]=="GHS Classification (UNECE)"){
      return(i)
    }
          
  }
}
hazards_retriever<-function(index,result_json_object){
  result<-result_json_object
  hierarchy<-result[["result"]][["Hierarchies"]][["Hierarchy"]][[index]]
  i<-1
  output_list<-rep(NA,length(hierarchy[["Node"]]))
  while(str_detect(hierarchy[["Node"]][[i]][["Information"]][["Name"]],"H") & 
        i<length(hierarchy[["Node"]])){
    output_list[i]<-hierarchy[["Node"]][[i]][["Information"]][["Name"]]
    i<-i+1
  }
  return(output_list[!is.na(output_list)])
}
```


Find the most common chemical
```{r}
most_frequent_chem <- straw %>%
  group_by(type, chem_name) %>%
  summarise(count = n(), .groups = 'drop') %>%
  group_by(type) %>%
  filter(count == max(count)) %>%
  arrange(desc(count))
```




```{r}
chemical_vec<-c("ABAMECTIN", "CYPRODINIL","FLUDIOXONIL")

result_f<-get_pug_rest(identifier = "FLUDIOXONIL", namespace = "name", domain = "compound",
                       operation="classification", output = "JSON")

hazards_retriever(GHS_searcher(result_f),result_f)


result_c<-get_pug_rest(identifier = "CYPRODINIL", namespace = "name", domain = "compound",
                       operation="classification", output = "JSON")

hazards_retriever(GHS_searcher(result_c),result_c)

result_a<-get_pug_rest(identifier = "ABAMECTIN", namespace = "name", domain = "compound",
                       operation="classification", output = "JSON")

hazards_retriever(GHS_searcher(result_a),result_a)

```


I get the hazard data for the most common chemical
```{r}
library(PubChemR)
chemical_vec <- c("ABAMECTIN", "CYPRODINIL", "FLUDIOXONIL")
get_ghs_info <- function(chemical_name) {
  result <- get_pug_rest(identifier = chemical_name, namespace = "name", domain = "compound", 
                         operation = "classification", output = "JSON")
  ghs_index <- GHS_searcher(result)
  
  if (!is.null(ghs_index)) {
    hazards <- hazards_retriever(ghs_index, result)
    return(paste(hazards, collapse = ", "))
  } else {
    return("No GHS Information Found")
  }
}
hazards_data <- data.frame(
  Chemical = character(),
  Hazards = character(),
  stringsAsFactors = FALSE
)
for (chemical in chemical_vec) {
  ghs_info <- get_ghs_info(chemical)
  hazards_data <- rbind(hazards_data, data.frame(Chemical = chemical, Hazards = ghs_info, stringsAsFactors = FALSE))
}
print(hazards_data)
```




Now I count the hazard.
```{r}
hazard_counts <- hazards_data %>%
  separate_rows(Hazards, sep = ",\\s*") %>%
  mutate(Hazard_Code = sub(":.*", "", Hazards)) %>%
  filter(grepl("^H\\d+", Hazard_Code)) %>%
  count(Hazard_Code, sort = TRUE)
print(hazard_counts)
```

According to the information I get from GHS, H300 and H400 are high hazard codes:
H300: Acute toxicity, highly lethal.
H400: Very toxic to aquatic life.

H410 and H317 also belong to a less hazard level:
H410: Very toxic to aquatic life with long-lasting effects.
H317: May cause an allergic skin reaction.

ABAMECTIN contains H300 and H400, and Abamectin is most common in INSECTICIDE, so from the graph for INSECTICIDE we can see
it's used more in Florida than California, which means strawberry from California may healther than strawberry from Florida.

For CYPRODINIL and FLUDIOXONIL, harzard in Cyprodinil contains H317 which be considered as less harzard level than H300 and H400,
and Fludioxonil contains H410 wich is very toxic to aquatic life but strawberry is not aquatic life.



In this paper I ask some help from Chatgpt for unerstanding how to use GHS_searcher.
